Local Spectral Clustering of Density Upper Level Sets

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Sentence added by Alden

To the best of our knowledge, Theorem \ref{thm: mixing_time_upper_bound} is the
first bound, albeit asymptotic, on the mixing time of random walks over
neighborhood graphs which is independent of $n$, the number of vertices.

>>>>

The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
analogous mixing time bounds developed for the mixing time of the
continuous-space ball walk over convex sets. To the best of our knowledge, our
result is the first bound, albeit asymptotic, on the mixing time of random walks
over neighborhood graphs that is independent of $n$, the number of vertices.
